Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-04-23 pldi14/macros_part2.tex
Misc
Also number slogans

% Theorems, lemmas, corollaries
% Typeset in roman to avoid known TeX feature
% (bad spacing between italic text and math formulas)
%
% Numbering:
% Theorem 3.1. It always rains.
% Lemma 3.2. If it rains, then the weather is bad.
% Corollary 3.3. The weather is always bad.
%
% http://tex.stackexchange.com/a/67251
\theoremstyle{definition}
% \input{pldi14/QED}
\theoremsymbol{\ensuremath{_\Box}}
\declaretheorem[numberwithin=section,refname={Theorem,Theorems}]{theorem}
\declaretheorem[numberlike=theorem,refname={Lemma,Lemmas}]{lemma}
\declaretheorem[numberlike=theorem,refname={Corollary,Corollaries}]{corollary}
\declaretheorem[numberlike=theorem,refname={Definition,Definitions}]{definition}
% \declaretheorem[numberlike=theorem,name=Plugin Requirement]{parameter}
\declaretheorem[numberlike=theorem,name=Plugin Requirement,refname={Plugin Requirement,Plugin Requirements}]{requirement}
% \newtheorem{theorem}{Theorem}
% % http://tex.stackexchange.com/a/45358/1340
% % \numberwithin{section}{chapter} % From AMS Author FAQ (http://www.ams.org/faq?class_id=561), makes no difference?
%\numberwithin{theorem}{section}
% \newtheorem{lemma}[theorem]{Lemma}
% \newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{definition}[theorem]{Definition}
% \newtheorem{parameter}[theorem]{Plugin Requirement}

>>>>

% Theorems, lemmas, corollaries
% Typeset in roman to avoid known TeX feature
% (bad spacing between italic text and math formulas)
%
% Numbering:
% Theorem 3.1. It always rains.
% Lemma 3.2. If it rains, then the weather is bad.
% Corollary 3.3. The weather is always bad.
%
% http://tex.stackexchange.com/a/67251
\theoremstyle{definition}
% \input{pldi14/QED}
\theoremsymbol{\ensuremath{_\Box}}
\declaretheorem[numberwithin=section,refname={Theorem,Theorems}]{theorem}
\declaretheorem[numberlike=theorem,refname={Lemma,Lemmas}]{lemma}
\declaretheorem[numberlike=theorem,refname={Corollary,Corollaries}]{corollary}
\declaretheorem[numberlike=theorem,refname={Definition,Definitions}]{definition}
% \declaretheorem[numberlike=theorem,name=Plugin Requirement]{parameter}
\declaretheorem[numberlike=theorem,name=Plugin Requirement,refname={Plugin Requirement,Plugin Requirements}]{requirement}
\declaretheorem[numberlike=theorem,name=Remark,refname={Remark,Remarks}]{remark}
\declaretheorem[numberlike=theorem,name=Example,refname={Example,Examples}]{examples}
\declaretheorem[numberlike=theorem,name=Example,refname={Example,Examples}]{example}
\declaretheorem[numberlike=theorem,name=Slogan,refname={Slogan,Slogans}]{slogan}

% \newtheorem{theorem}{Theorem}
% % http://tex.stackexchange.com/a/45358/1340
% % \numberwithin{section}{chapter} % From AMS Author FAQ (http://www.ams.org/faq?class_id=561), makes no difference?
%\numberwithin{theorem}{section}
% \newtheorem{lemma}[theorem]{Lemma}
% \newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{definition}[theorem]{Definition}
% \newtheorem{parameter}[theorem]{Plugin Requirement}
